多變量分析 HW3

### 2018-05-07 1062_class/Multivariate_Analysis/HW3_factor_analysis/HW3.Rmd
up

```{r setup, include=FALSE}
if (knitr::is_html_output()) {
    knitr::opts_chunk$set(
	echo = FALSE,
	fig.dim = c(3.6, 3.2),
	message = FALSE,
	warning = FALSE,
	comment = "",
	dev = "svg",
	out.width = "70%"
)
} else {
    knitr::opts_chunk$set(echo = FALSE,
                          message=FALSE,
                          warning=FALSE,
                          comment = "",
                          out.width = '70%')
}
options(digits = 4)
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(mat2tex)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
source("multivariate_fc.R")
```

@@

Q2: 9.32
====================================
```{r}
library(readr)
library(psych)
bulls <- read_table2("T1-10.dat", col_names = FALSE)
colnames(bulls) <- c("Breed", "SalePr", "YrHgt", 
                     "FtFrBody", "PrctFFB", "Frame",
                     "BkFat", "SaleHt", "SaleWt")
bulls <- bulls[,-c(1,9)]
source("fa_functions.R") # for formating loading mt
```

## (a) S PC
```{r}
fa_S_pc <- principal(bulls, 
              nfactors = 2, 
              rotate = 'varimax', 
              covar = TRUE)
fa_S_pc[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 30, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

@@

```{r}
fa_S_ml <- fa(bulls, nfactors=2, 
              rotate="varimax", covar = T,
              fm="ml", scores="regression")
fa_S_ml[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 30, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

@@

```{r}
fa_R_pc <- principal(bulls, 
              nfactors = 2, 
              rotate = 'varimax', 
              covar = F)
fa_R_pc[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 0.65, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

## (d) R ML
```{r}
fa_R_ml <- fa(bulls, nfactors=2, 
              rotate="varimax", covar = F, 
              fm="ml", scores="regression")
fa_R_ml[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 0.6, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

@@

```{r}
fa_R_pc2[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 0.5, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

@@

```{r}
data <- cbind(fa_R_pc2[["scores"]], as.factor(drinks$BRAND)) %>%
    as.data.frame()
colnames(data) <- c("F1", "F2", "F3", "F4", "Brand")

data[data$Brand =="1", "Brand"] <- "Pepsi"
data[data$Brand =="2", "Brand"] <- "Coke"
data[data$Brand =="3", "Brand"] <- "Gatorade"
data[data$Brand =="4", "Brand"] <- "Allsport"
data[data$Brand =="5", "Brand"] <- "Lipton tea"
data[data$Brand =="6", "Brand"] <- "Nestea"
```

```{r out.width="50%", fig.show='hold'}
### F1, F2
ggplot(data[,c(1,2, 5)]) +
    geom_point(aes(x=F1, y=F2, color=Brand))

### F1, F3
ggplot(data[,c(1,3, 5)]) +
    geom_point(aes(x=F1, y=F3, color=Brand))
```

```{r out.width="50%", fig.show='hold'}
### F1, F4
ggplot(data[,c(1,4, 5)]) +
    geom_point(aes(x=F1, y=F4, color=Brand))

### F2, F3
ggplot(data[,c(2,3, 5)]) +
    geom_point(aes(x=F2, y=F3, color=Brand))
```

```{r out.width="50%", fig.show='hold'}
### F2, F4
ggplot(data[,c(2,4, 5)]) +
    geom_point(aes(x=F2, y=F4, color=Brand))

### F3, F4
ggplot(data[,c(3,4, 5)]) +
    geom_point(aes(x=F3, y=F4, color=Brand))
```

>>>>

```{r setup, include=FALSE}
if (knitr::is_html_output()) {
    knitr::opts_chunk$set(
	echo = TRUE,
	fig.dim = c(3.6, 3.2),
	message = FALSE,
	warning = FALSE,
	comment = "",
	dev = "svg",
	out.width = "70%"
)
} else {
    knitr::opts_chunk$set(echo = FALSE,
                          message=FALSE,
                          warning=FALSE,
                          comment = "",
                          out.width = '70%')
}
options(digits = 4)
library(readr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(mat2tex)
theme <- theme(axis.text.x = element_text(size = 7, face = "plain", angle = 30),
               axis.text.y = element_text(size = 7, face = "plain"),
               axis.title.x = element_text(size = 9, face = "bold"),
    axis.title.y = element_text(size = 9, face = "bold"))
source("multivariate_fc.R")
```

@@

Q2: 9.32
====================================
```{r}
library(readr)
library(psych)
bulls <- read_table2("T1-10.dat", col_names = FALSE)
colnames(bulls) <- c("Breed", "SalePr", "YrHgt", 
                     "FtFrBody", "PrctFFB", "Frame",
                     "BkFat", "SaleHt", "SaleWt")
bulls <- bulls[,-c(1,2)]
source("fa_functions.R") # for formating loading mt
```

## (a) S PC
```{r}
fa_S_pc <- principal(bulls, 
              nfactors = 3, 
              rotate = 'varimax', 
              covar = TRUE)
fa_S_pc[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 30, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

@@

```{r}
fa_S_ml <- fa(bulls, nfactors=3, 
              rotate="varimax", covar = T,
              fm="ml", scores="regression")
fa_S_ml[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 30, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

@@

```{r}
fa_R_pc <- principal(bulls, 
              nfactors = 3, 
              rotate = 'varimax', 
              covar = F)
fa_R_pc[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 0.65, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

## (d) R ML
```{r}
fa_R_ml <- fa(bulls, nfactors=3, 
              rotate="varimax", covar = F, 
              fm="ml", scores="regression")
fa_R_ml[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 0.6, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

@@

```{r}
source("fa_functions.R")
fa_R_pc2[["loadings"]][,] %>% round(3) %>%
    format_loading_matrix(criterion = 0.5, markdown = T) %>%
    kable("markdown",align = 'c', escape = F)
```

@@

```{r out.width="50%", fig.show='hold'}
avg_fs <- cbind(avg_fs, rownames(avg_fs))
colnames(avg_fs) <- c("F1", "F2", "F3", "F4", "Brand")

### F1, F2
ggplot(avg_fs[,c(1,2, 5)],aes(x=F1, y=F2, color=Brand)) +
    geom_point() +
    geom_text(aes(label=Brand),
              hjust=0.5, vjust=-0.4, size = 3) +
    theme(legend.position = 'none')

### F1, F3
ggplot(avg_fs[,c(1,3, 5)],aes(x=F1, y=F3, color=Brand)) +
    geom_point() +
    geom_text(aes(label=Brand),
              hjust=0.5, vjust=-0.4, size = 3) +
    theme(legend.position = 'none')
```

```{r out.width="50%", fig.show='hold'}
### F1, F4
ggplot(avg_fs[,c(1,4, 5)],aes(x=F1, y=F4, color=Brand)) +
    geom_point() +
    geom_text(aes(label=Brand),
              hjust=0.5, vjust=-0.4, size = 3) +
    theme(legend.position = 'none')

### F2, F3
ggplot(avg_fs[,c(2,3, 5)], aes(x=F2, y=F3, color=Brand)) +
    geom_point() +
    geom_text(aes(label=Brand),
              hjust=0.5, vjust=-0.4, size = 3) +
    theme(legend.position = 'none')
```

```{r out.width="50%", fig.show='hold'}
### F2, F4
ggplot(avg_fs[,c(2,4, 5)],aes(x=F2, y=F4, color=Brand)) +
    geom_point() +
    geom_text(aes(label=Brand),
              hjust=0.5, vjust=-0.4, size = 3) +
    theme(legend.position = 'none')

### F3, F4
ggplot(avg_fs[,c(3,4, 5)], aes(x=F3, y=F4, color=Brand)) +
    geom_point() +
    geom_text(aes(label=Brand),
              hjust=0.5, vjust=-0.4, size = 3) +
    theme(legend.position = 'none')
```
